### 2021-07-12 src/paper/data/number_of_contacts.tex
Use parameter notation everywhere in the data section.

We calibrate the parameters for the predicted numbers of contacts from contact diaries of
over 2000 individuals from Germany, Belgium, the Netherlands and Luxembourg
\citep{Mossong2008}. Each contact diary contains all contacts an individual had
throughout one day, including information on the other person (such as age and gender)
and information on the contact. Importantly, for each contact individuals entered of
which type the contact (school, leisure, work etc.) was and how frequent the contact with
the other person is. Binning the number of contacts for very high numbers, we arrive at
the distributions of the numbers of contacts by contact type as shown in Figure~\ref{fig:n_contacts}.

@@

    \caption{Number of Contacts of the Different Contact Types}
    \label{fig:n_contacts}
    \floatfoot{\noindent
        \textit{Note:} This figure shows the pre-pandemic number of contacts individuals
        report of different contact types.
        % non recurrent contacts
        In the model it is sampled every day which of the numbers of non recurrent
        contacts a person is planned to have. Note that the contact diaries include such
        high values that super spreading events are well possible in our model through
        non recurrent models.
        % recurrent contacts
        For recurrent contacts individuals are put into groups that meet either every day
        or on a particular week day every day. For work contacts, meetings can only take
        place on work days.
        % reductions that can happen
        The pre-pandemic number of contacts with transmission potential is reduced by
        policies, seasonality and individual responses to events such as
        receiving a positive rapid test to the number of actual contacts with
        transmission potential.
        % other
        The upper row shows the distribution of the number of other contacts individuals
        report. Other contacts include all contacts that are not household members,
        school contacts or work contacts, for example leisure contacts. We assume that
        individuals in households with children or teachers or retired individuals have
        additional non recurrent other contacts during school vacations to cover things
        like family visits or travel during vacations.
        % work contacts
        The lower row shows the distribution of the different types of work contacts.
        Work contacts only take place between working individuals.}
\end{figure}

>>>>

We calibrate the parameters for the predicted numbers of contacts from contact diaries of
over 2000 individuals from Germany, Belgium, the Netherlands and Luxembourg
\citep{Mossong2008}. Each contact diary contains all contacts an individual had
throughout one day, including information on the other person (such as age and gender)
and information on the contact. Importantly, for each contact individuals entered of
which type the contact (school, leisure, work etc.) was and how frequent the contact with
the other person is. Binning the number of contacts for very high numbers, we arrive at
the distributions of the numbers of contacts by type of contact ($\eta_{c}$) as shown in
Figure~\ref{fig:n_contacts}.

@@

    \caption{Number of Contacts of the Different Contact Types}
    \label{fig:n_contacts}
    \floatfoot{\noindent
        \textit{Note:} This figure shows the pre-pandemic number of contacts individuals
        report of different contact types ($\eta_c$).
        % non recurrent contacts
        In the model it is sampled every day which of the numbers of non recurrent
        contacts a person is planned to have. Note that the contact diaries include such
        high values that super spreading events are well possible in our model through
        non recurrent models.
        % recurrent contacts
        For recurrent contacts individuals are put into groups that meet either every day
        or on a particular week day every day. For work contacts, meetings can only take
        place on work days.
        % reductions that can happen
        The pre-pandemic number of contacts with transmission potential is reduced by
        policies ($\rho$), seasonality ($\kappa$) and individual responses ($\tau$) to
        events such as receiving a positive rapid test to the number of actual contacts
        with transmission potential.
        % other
        The upper row shows the distribution of the number of other contacts individuals
        report ($\eta_{other}$). Other contacts include all contacts that are not
        household members, school contacts or work contacts, for example leisure
        contacts. We assume that individuals in households with children or teachers or
        retired individuals have additional non recurrent other contacts during school
        vacations to cover things like family visits or travel during vacations.
        % work contacts
        The lower row shows the distribution of the different types of work contacts
        ($\eta_{work}$). Work contacts only take place between working individuals.}
\end{figure}

### 2021-07-12 src/paper/data/policies.tex
Use parameter notation everywhere in the data section.

Our policies usually affect one of our four contact types: households, education, work
and other contacts.
% households
For households we assume that the individuals' contacts in their households do not change
over our estimation period.
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and rotating schooling
schedules where only one half of students attends every other week or day.% For the moment we ignore that lack of childcare leads working parents to stay home.
An approximation of the share of contacts still taking place with the different school
regulations can be found in Figure~\ref{fig:school_multiplier}.
% work
For work contacts we use the reductions in work mobility reported by the Google Mobility
Data \citep{Google2021} to calibrate our work policies. Reductions in work contacts are
not random but governed through a work contact priority where the policy changes the
threshold below which workers stay home. Figure \ref{fig:work_multiplier} shows the share
of workers that go to work over time at the federal German level. We use the data on the
state level to account for local holidays and differences in state regulations.
% hygiene umltiplier
In addition, for both work and school contacts we assume that hygiene measures (such as
masks, ventilation and hand washing) became more strict and more conscientiously observed
in November, leading to a reduction of 33\% in the number of contacts with the potential
to transmit Covid-19.

@@

    \floatfoot{\noindent \textit{Note:} The left figure shows the approximate share of
    school contacts taking place with and without vacations factored in. The dates on
    which schools have vacation are decided at the state level. Vacations are directly
    implemented in our model with no school contacts taking place on weekends and during
    vacations (by federal state) just like the schooling mode (full operation, emergency
    care, rotating schemes with half class sizes etc.). The figure is thus only an
    illustration that shows the approximate share of contacts taking place compared to
    the pre-pandemic level with and without vacations. The difference between the lines
    show when vacations take place and to what degree. For example all states have fall
    vacations but the timing varies strongly between states while all states close
    schools during the Christmas holidays. The right figure shows the work mobility as
    reported by \cite{Google2021}. We take this as a proxy of the share of workers who
    still have physical work contacts. The figure interpolates over weekends as we handle
    weekend effects through information on work on weekends in the German census data we
    use. The figure shows the share for Germany as a whole. To capture the effect that
    local policies, school vacations, etc. have on work contacts we use the data on the
    state level to determine which workers go to work depending on the state they live
    in.}
    \label{fig:multipliers}
\end{figure}

Lastly, for the other contacts category we could not calibrate the policies from data but
estimated the policy effects. The estimation and values are detailed in
Section~\ref{subsec:estimated_params} and Figure~\ref{fig:other_multiplier}.

>>>>

Our policies (denoted by $\rho$) usually affect one of three contact types: education,
work and other contacts.
% households
Germany had no policies limiting contacts within households so there are no policies on
them in our model.\footnote{Household contacts can, however, be reduced when individuals
quarantine themselves after developing symptoms, for example. This happens to a lesser
degree than other contacts to capture difficulties in isolation within the home.}
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and rotating schooling
schedules where only one half of students attends every other week or day.
% For the moment we ignore that lack of childcare leads working parents to stay home.
An approximation of the share of contacts still taking place with the different school
regulations can be found in Figure~\ref{fig:school_multiplier}.
% work
For work contacts we use the reductions in work mobility reported by the Google Mobility
Data \citep{Google2021} to calibrate the reduction in physical work contacts
($\rho_{w,\:attend,\:t}$). Reductions in work contacts are not random but governed
through a work contact priority where the policy changes the threshold below which
workers stay home. Figure \ref{fig:work_multiplier} shows the share of workers that go to
work over time at the federal German level. We use the data on the state level to account
for local holidays and differences in state regulations.
% hygiene umltiplier
In addition, for both work and school contacts we assume that hygiene measures (such as
masks, ventilation and hand washing) became more strict and more conscientiously observed
in November, leading to a reduction of 33\% in the number of contacts with the potential
to transmit Covid-19 ($\rho_{hygiene}$).

@@

    \floatfoot{\noindent \textit{Note:} The left figure shows the approximate share of
    school contacts taking place with and without vacations factored in. The dates on
    which schools have vacation are decided at the state level. Vacations are directly
    implemented in our model with no school contacts taking place on weekends and during
    vacations (by federal state) just like the schooling mode (full operation, emergency
    care, rotating schemes with half class sizes etc.). The figure is, thus, only an
    illustration that shows the approximate share of contacts taking place compared to
    the pre-pandemic level with and without vacations. The difference between the lines
    show when vacations take place and to what degree. For example all states have fall
    vacations but the timing varies strongly between states while all states close
    schools during the Christmas holidays. The right figure shows the work mobility as
    reported by \cite{Google2021}. We take this as a proxy of the share of workers who
    still have physical work contacts ($\rho_{w,\:attend,\:t}$). The figure interpolates
    over weekends as we handle weekend effects through information on work on weekends in
    the German census data we use. The figure shows the share for Germany as a whole. To
    capture the effect that local policies, school vacations, etc. have on work contacts
    we use the data on the state level to determine which workers go to work depending on
    the state they live in.}
    \label{fig:multipliers}
\end{figure}

Lastly, for the other contacts category ($\rho_{other,\:t}$) we could not calibrate the
policies from data but estimated the policy effects. The estimation and values are
detailed in Section~\ref{subsec:estimated_params} and Figure~\ref{fig:other_multiplier}.

### 2021-07-12 src/paper/data/rapid_test_demand.tex
Make data section on share known cases ready for review. Add figures showing the parameter demand shares in different robustness scenarios.
Fixed document, some typos, removed duplicated parameter.
Use parameter notation everywhere in the data section.

In our model, there are five reasons why rapid tests are done:\comment[id=J]{ Add a
    section on how we calibrate rapid test demand; Mainly describe the datapoints we have
    and say that we usually interpolate linearly in between data points. (Only exception
    to that is private rapid test demand, which we fit to data)
}

@@

For work contacts, we know from the COSMO study (\cite{Betsch2021}, 20th/21st of April)
that 60\% of workers who receive a test offer by their employer regularly use it. We
assume this share to be time constant.

In addition, there are some surveys that allow us to trace the expansion of employers who
offer tests to their employees. Mid march, 20\% of employers offered tests to their
employees \citep{DIHK2021}. In the second half of March, 23\% of employees reported being
offered weekly rapid tests by their employer \citep{Ahlers2021}. This share increased to
61\% until the first days of April \citep{BMWI2021, IZA2021}.

Until mid April 72\% of workers were expected to receive a weekly test offer
\citep{BMWI2021, IZA2021}. However, according to surveys conducted in mid April
\citep{Betsch2021}, less than two thirds of individuals with work contacts receive a test
offer. Starting on April 19th employers were required by law to provide two weekly tests
to their employees \citep{Bundesanzeiger2021}. We assume that compliance is incomplete
and only 80\% of employers actually offer tests. We interpolate between these points
linearly, arriving at the blue line in Figure~\ref{fig:rapid_test_demand}.

@@

We assume that employees in educational facilities start getting tested in 2021 and that
by March 1st 30\% of them are tested weekly. The share increases to 90\% for the week
before Easter. At that time both Bavaria \citep{STMGP2021} and Baden-Württemberg
\citep{MinisteriumKultus2021} were offering tests to teachers and North-Rhine Westphalia
\citep{SchulministeriumNRW2021} and Lower Saxony \citep{NSMK2021} were already testing
students and tests for students and teachers were already mandatory in Saxony
\citep{SMK2021}. After Easter we assume that 95\% of teachers get tested twice per week.

Tests for students started later \citep{MinisteriumKultus2021, SchulministeriumNRW2021}
so we assume that they only start in February and only 10\% of students get tested by
March 1st. Relying on the same sources as above we approximate that by the week before
Easter this share had increased to 40\% \citep{SchulministeriumNRW2021}.

After Easter the share of students receiving twice weekly tests is set to 75\%. This is
based on tests becoming mandatory in Bavaria \citep{BayerischeStaatskanzlei2021} and
North Rhine-Westphalia \citep{SchulministeriumNRW2021b} after their Easter breaks and on
the 19th in Baden-Württemberg \citep{KMBaWue2021}. Again, we interpolate linearly between
these points and arrive at the purple line for teachers and the red line for school
students in Figure~\ref{fig:rapid_test_demand}.

@@

To limit our degrees of freedom, we only have one parameter that governs how many
individuals do a rapid test because of any of the private demand reasons (own symptoms
but no PCR test, planned weekly leisure meeting or a symptomatic or positively tested
household member).

We assume that there is no private rapid test demand until March when both the citizens'
tests and rapid tests for lay people started to become available
\citep{Bundesanzeiger2021a, Bundesregierung2021} and other access to rapid tests was very
limited.

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior, we take this as
the upper bound of private rapid test demand which we estimate in our model to be reached
in the beginning of May. To cover that many people are likely to have sought and done
their first rapid test before the Easter holidays we add another point that we estimate
for the rapid test demand around Easter. Similarly, we estimate one point in mid March
when tests started to become available in grocery stores and pharmacies which we estimate
in our model. The resulting share of private rapid test demand is shown as the green line
in Figure~\ref{fig:rapid_test_demand}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{Share of Individuals Doing a Rapid Test.}
    \label{fig:rapid_test_demand}
    \floatfoot{\noindent \textit{Note:} Rapid test demand can be triggered by individuals
    planning to have education contacts, work contacts, developing symptoms without
    access to a PCR test, having a household member with a positive test or symptoms. In
    each case whether a rapid test is done depends on how long it has been since the
    individual's last rapid test and her individual compliance parameter. As an example,
    take a worker in May. In that time workers are encouraged to test themselves twice
    weekly but there is no general requirement to test themselves. If the worker has not
    done a test within the last four days in our model she will demand a test if her
    (time-constant) compliance parameter belongs to the upper 60\% in the population.}
    \label{fig:rapid_test_demand}
\end{figure}

>>>>

In our model, there are five reasons why rapid tests are done:

@@

For work contacts, we know from the COSMO study (\cite{Betsch2021}, 20th/21st of April)
that 60\% of workers who receive a test offer by their employer regularly use it
($\pi_{w,\:d}$). We assume this share to be time constant.

In addition, there are some surveys that allow us to trace the expansion of employers who
offer tests to their employees ($\pi_{w,\:s,\:t}$). Mid march, 20\% of employers offered
tests to their employees \citep{DIHK2021}. In the second half of March, 23\% of employees
reported being offered weekly rapid tests by their employer \citep{Ahlers2021}. This
share increased to 61\% until the first days of April \citep{BMWI2021, IZA2021}. Until
mid April 72\% of workers were expected to receive a weekly test offer \citep{BMWI2021,
IZA2021}. However, according to surveys conducted in mid April \citep{Betsch2021}, less
than two thirds of individuals with work contacts receive a test offer. Starting on April
19th employers were required by law to provide two weekly tests to their employees
\citep{Bundesanzeiger2021}. We assume that compliance is incomplete and only 80\% of
employers actually offer tests. We interpolate between these points linearly, arriving at
the blue line in Figure~\ref{fig:rapid_test_demand}. In addition, we increase the
frequency of testing ($\theta_{t,\:work}$) from weekly to twice weekly during April.

@@

We assume that employees in educational facilities start getting tested in 2021 and that
by March 1st 30\% of them ($\pi_{teacher,\:t}$) are tested weekly
($\theta_{before\:Easter,\:educ} = 7$). The share increases to 90\% for the week before
Easter. At that time both Bavaria \citep{STMGP2021} and Baden-Württemberg
\citep{MinisteriumKultus2021} were offering tests to teachers and North-Rhine Westphalia
\citep{SchulministeriumNRW2021} and Lower Saxony \citep{NSMK2021} were already testing
students and tests for students and teachers were already mandatory in Saxony
\citep{SMK2021}. After Easter we assume that 95\% of teachers get tested twice per week
($\theta_{after\:Easter,\:educ} = 3$).

Tests for students started later \citep{MinisteriumKultus2021, SchulministeriumNRW2021}
so we assume that they only start in February and only 10\% of students get tested by
March 1st ($\pi_{students,\:t}$). Relying on the same sources as above we approximate
that by the week before Easter this share had increased to 40\%
\citep{SchulministeriumNRW2021}. After Easter the share of students receiving twice
weekly tests is set to 75\%. This is based on tests becoming mandatory in Bavaria
\citep{BayerischeStaatskanzlei2021} and North Rhine-Westphalia
\citep{SchulministeriumNRW2021b} after their Easter breaks and on the 19th in
Baden-Württemberg \citep{KMBaWue2021}, after which we assume twice weekly rapid tests to
be mandatory for all students in Germany. Again, we interpolate linearly between these
points and arrive at the purple line for teachers and the red line for school students in
Figure~\ref{fig:rapid_test_demand}.

@@

To limit our degrees of freedom, we only have one parameter that governs how many
individuals do a rapid test because of any of the private demand reasons
($\pi_{private,\:t}$).\footnote{The reasons that can lead to an individual doing a rapid
test for private reasons are own symptoms but no PCR test, planned weekly leisure meeting
or a symptomatic or positively tested household member}
We assume that there is no private rapid test demand until March when both the citizens'
tests and rapid tests for lay people started to become available
\citep{Bundesanzeiger2021a, Bundesregierung2021} and other access to rapid tests was very
limited.

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior, we take this as
the upper bound of private rapid test demand which we estimate in our model to be reached
in the beginning of May. To cover that many people are likely to have sought and done
their first rapid test before the Easter holidays we add another point that we estimate
for the rapid test demand around Easter. Similarly, we estimate one point in mid March
when tests started to become available in grocery stores and pharmacies which we estimate
in our model. The resulting share of private rapid test demand is shown as the green line
in Figure~\ref{fig:rapid_test_demand} (also see Section~\ref{subsec:estimated_params} for
details on the estimation).

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/results/figures/data/testing/rapid_test_demand/baseline_shares}
    \caption{Share of Individuals Doing a Rapid Test.}
    \floatfoot{\noindent \textit{Note:} Rapid test demand can be triggered by individuals
    planning to have education contacts ($\pi_{teacher,\:t}$ or $\pi_{students,\:t}$),
    work contacts ($\pi_{w,\:d}$ and $\pi_{w,\:s,\:t}$), developing symptoms without
    access to a PCR test, having a household member with a positive test or symptoms
    ($\pi_{private,\:t}$). In each case whether a rapid test is done depends on how long
    it has been since the individual's last rapid test and her individual compliance
    parameter. As an example, take a worker in May. In that time workers are encouraged
    to test themselves twice weekly (or every three days, i.e. $\theta_{May,\:work} = 3$)
    but there is no general requirement to test themselves. If the worker has not done a
    test within the last four days in our model she will demand a test if her
    (time-constant) compliance parameter belongs to the upper 60\% in the population.}
    \label{fig:rapid_test_demand}
\end{figure}

### 2021-07-12 src/paper/data/share_known_cases.tex
Use parameter notation everywhere in the data section.

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see
Section~\ref{sub:testing} for a detailed description for how we model both rapid and PCR
tests). For our model it is important to have an estimate for the share of cases that is
detected in the absence of rapid tests. For this we rely on the Dunkelzifferradar Project
\citep{Dunkelzifferradar2020} which relies on estimates of the case fatality rate to
estimate the number of total cases given the number of CoViD-19 deaths which are assumed
to be perfectly observable. For 2020, we follow the reported share of detected cases
quite closely only interpolating the phase of November 2020 where the testing policy was
changed to give more priority to vulnerable groups. This lead to more tests being done
among older age groups which are also at the highest risk of dying from CoViD-19 and an
overestimation of the share of detected cases.
% After Christmas 2020
Since vaccinations started after Christmas 2020 and these were predominantly given to
nursing homes in the beginning and other vulnerable groups in spring, we expect the
relationship between deaths and the number of total infections to change rapidly in 2021.
This is why we stop using the share of detected cases estimated by the Dunkelzifferradar
after Christmas. Instead, we assume that the share of detected cases would have
stayed the same in the absence of rapid tests. Thus, we also achieve in our model an
increase in the share of detected cases but this is driven from inside our model through
increased rapid testing and follow-up on positive rapid tests (see
Section~\ref{subsec:results_share_known_cases} and \ref{sub:testing}).
% Christmas and Easter
Lastly, we model reductions in the share known cases due to the two major holidays in our
simulation period, Christmas and Easter. During both holidays many laboratories did not
process tests and most physicians' offices were closed, leading to less PCR tests and
short and large drops in the share of known cases. The resulting share of detected cases
in the absence of rapid tests is shown in Figure~\ref{fig:share_known_cases_data}.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/data/testing/assumed_overall_share_known_cases}
  \caption{Share of Detected Cases in the Absence of Rapid Tests}
  \label{fig:share_known_cases_data}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the
  \citet{Dunkelzifferradar2020} for all of 2020 and
  then assume it to be constant as vaccinations of the elderly strongly affect the case
  fatality rate which the project does not account for. Starting in 2021 in addition to
  the overall numbers of detected cases through symptoms and the share known cases, cases
  are also detected through confirmation of positive rapid tests which happens
  endogenously inside the model. For the public holidays of Christmas and Easter we lower
  the share of detected cases as fewer PCR tests are available during public holidays.}
\end{figure}

>>>>

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see
Section~\ref{sub:testing} for a detailed description for how we model both rapid and PCR
tests). For our model it is important to have an estimate for the share of cases that is
detected in the absence of rapid tests ($\psi_t$). For this we rely on the
\cite[Dunkelzifferradar Project][]{Dunkelzifferradar2020} which uses estimates of the case
fatality rate to estimate the number of total cases given the number of CoViD-19 deaths
which are assumed to be perfectly observable. For 2020, we follow the reported share of
detected cases quite closely \textcolor{red}{only interpolating the phase of November
2020 where the testing policy was changed to give more priority to vulnerable groups
\citep{RKI2020a}. This lead to more tests being done among older age groups which are
also at the highest risk of dying from CoViD-19. We suspect that this led the estimated
share of detected cases to increase without a corresponding increase in the share of
detected cases in the overall population as PCR tests, a rare resource at the time, were
only moved to groups with a high case fatality ratio.}

% After Christmas 2020
Since vaccinations started after Christmas 2020 and these were predominantly given to
nursing homes in the beginning and other vulnerable groups in spring, we expect the
relationship between deaths and the number of total infections to change rapidly in 2021.
This is why we stop using the share of detected cases estimated by the Dunkelzifferradar
after Christmas. Instead, we assume that the share of detected cases would have stayed
the same in the absence of rapid tests. Thus, we also achieve in our model an increase in
the share of detected cases but this is driven from inside our model through increased
rapid testing which lead follow-up PCR tests when they are positive (see
Section~\ref{subsec:results_share_known_cases} and \ref{sub:testing}).

% Christmas and Easter
Lastly, we model reductions in the share known cases due to the two major holidays in our
simulation period, Christmas and Easter. During both holidays many laboratories did not
process tests and most physicians' offices were closed, leading to less PCR tests and
short and large drops in the share of known cases. The resulting share of detected cases
in the absence of rapid tests is shown in Figure~\ref{fig:share_known_cases_data}.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/data/testing/assumed_overall_share_known_cases}
  \caption{Share of Detected Cases in the Absence of Rapid Tests}
  \label{fig:share_known_cases_data}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation. We use the overall share of known
  cases that was estimated through the case fatality ratio by the \cite[Dunkelzifferradar
  Project][]{Dunkelzifferradar2020} for all of 2020 and then assume it to be constant as
  vaccinations of the elderly strongly affect the case fatality rate which the project
  does not account for. Starting in 2021 in addition to the overall numbers of detected
  cases through symptoms and a random component, cases are also detected through
  confirmation of positive rapid tests which happens endogenously inside the model. For
  the public holidays of Christmas and Easter we lower the share of detected cases as
  fewer PCR tests are available during public holidays. See
  Figure~\ref{fig:share_known_cases_by_age_group} for how the share of detected cases
  develops in our model for each age group}.
\end{figure}

### 2021-07-12 src/paper/data/synthetic_population.tex
Use parameter notation everywhere in the data section.

% workers
Workers are assigned to a daily meeting work group. The group sizes vary to match the
number of daily repeating work contacts reported by working individuals in
\cite{Mossong2008}. These groups only consist of workers that work in the same county.
For a distribution of the number of daily recurring work contacts see
Figure~\ref{fig:n_contacts_work_daily_recurrent}. To match the number of weekly work groups
we match each worker with up to 14 other workers into pairs to match the number of
reported weekly work contacts shown in Figure~\ref{fig:n_contacts_work_weekly_recurrent}.
Each pair is assigned a weekday on which they always meet in the absence of work
policies. 80\% of these contacts are individuals from the same county.
% work contact priority
In the same way children have an educational priority determining if they are entitled to
emergency care workers are assigned a work contact priority that captures how necessary
their work is and to which degree they can work from home. This means that it's always
the same individuals that continue to have work contacts when work from home mandates of
a certain strictness are in place. We use the reduction in work mobility reported by
\cite{Google2021} as a proxy for the share of individuals that do not have work contacts.

@@

% individual responses
The individuals in our population can react to events such as developing symptoms that
are typical of CoViD-19, a positive PCR test or a positive rapid test by reducing their
contacts. To determine who would reduce their contacts in such a situation or demand a
rapid test we introduce a quarantine compliance parameter. Similarly we introduce a rapid
test compliance parameter that determines in which order individuals start demanding
rapid tests when rapid tests become increasingly available. This makes sure that when for
example only 10\% of workers get tested, it's the same workers that have access to tests
every week.

Lastly, for the distribution of vaccinations every individual is assigned a vaccination
group and a vaccination rank from that group that creates a complete vaccination queue
over the population including 15\% that refuse to be vaccinated as reported by the
Robert Koch Institute (RKI, \cite{RKI2021c}). The vaccination groups are created to
match the recommendations by the Ständige Impfkommission
\citep{VygenBonnet2020}.\footnote{We cover that teachers were prioritized more than
recommended by the commission.} To cover that the Pfizer-BioNTech vaccine was later
approved for younger age groups we put adolescents and children into two groups that
follow after the general population. These groups do not become eligible within our
simulation frame until June. The way vaccinations are rolled out in our model is shown
in Figure~\ref{fig:vaccinations_by_age_group}.

\begin{figure}[ht]   % vaccinations by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
  \caption{Vaccination Rates by Age Group}
  \floatfoot{\noindent \textit{Note:} An individual's vaccination priority depends on her
  work contact priority, her age group and a random component to capture medical
  preconditions like diabetes. 15\% of the population refuse to be vaccinated.
  Adolescents would be vaccinated after the general population and children last. The
  figure clearly shows that the first vaccinations go to some workers with very high work
  contact priority and to the 80 to 100 age group followed by the 60 to 79 year olds.
  Both groups are saturated with vaccinations by mid March and start of May respectively.
  By June a third of the younger adults have received the vaccination but these groups
  still remain far from herd immunity thresholds.}
  \label{fig:vaccinations_by_age_group}
\end{figure}

>>>>

% workers
Workers are assigned to a daily meeting work group. The group sizes vary to match the
number of daily repeating work contacts reported by working individuals in
\cite{Mossong2008}. These groups only consist of workers that work in the same county.
For a distribution of the number of daily recurring work contacts see
Figure~\ref{fig:n_contacts_work_daily_recurrent}. To match the number of weekly work groups
we match each worker with up to 14 other workers into pairs to match the number of
reported weekly work contacts shown in Figure~\ref{fig:n_contacts_work_weekly_recurrent}.
Each pair is assigned a weekday on which they always meet in the absence of work
policies. 80\% of these contacts are individuals from the same county.
% work contact priority
In the same way children have an educational priority determining if they are entitled to
emergency care workers are assigned a work contact priority that captures how necessary
their work is and to which degree they can work from home. This means that it's always
the same individuals that continue to have work contacts when work from home mandates of
a certain strictness are in place.

@@

% individual responses
The individuals in our population can react to events such as developing symptoms that
are typical of CoViD-19, a positive PCR test or a positive rapid test by reducing their
contacts. To determine who would reduce their contacts in such a situation or demand a
rapid test we introduce a quarantine compliance parameter. Similarly, we introduce a
rapid test compliance parameter that determines in which order individuals start
demanding rapid tests when rapid tests become increasingly available. This makes sure
that when for example only 10\% of workers get tested, it's the same workers that have
access to tests every week.

Lastly, for the distribution of vaccinations every individual is assigned a vaccination
group and a vaccination rank from that group that creates a complete vaccination queue
over the population including a share that refuses to be vaccinated ($\xi$) which we
calibrate to  15\% \citep{RKI2021c}. The vaccination groups are created to match the
recommendations by the Ständige Impfkommission \citep{VygenBonnet2020}.\footnote{We cover
that teachers were prioritized more than recommended by the commission.} To cover that
the Pfizer-BioNTech vaccine was later approved for younger age groups we put adolescents
and children into two groups that follow after the general population. These groups do
not become eligible within our simulation frame until June. The way vaccinations are
rolled out in our model is shown in Figure~\ref{fig:vaccinations_by_age_group}.

\begin{figure}[ht]   % vaccinations by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
  \caption{Vaccination Rates by Age Group}
  \floatfoot{\noindent \textit{Note:} An individual's vaccination priority depends on her
  work contact priority, her age group and a random component to capture medical
  preconditions like diabetes. 15\% of the population refuse to be vaccinated ($\xi$).
  Adolescents would be vaccinated after the general population and children last. The
  figure clearly shows that the first vaccinations go to some workers with very high work
  contact priority and to the 80 to 100 age group followed by the 60 to 79 year olds.
  Both groups are saturated with vaccinations by mid March and start of May respectively.
  By June a third of the younger adults have received the vaccination but these groups
  still remain far from herd immunity thresholds.}
  \label{fig:vaccinations_by_age_group}
\end{figure}
